\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-05-01 arch.tex
updates

A prime motivation behind the \rx architecture was to design a
controller which could bring automated planning closer to low-level
control of the vehicle while maintaining its reactivity.

Traditionally planning has been deemed computationally expensive with
planner performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for. In such a situation, the agent may thrash if
the internal state of the plan gets out of synch with the actual state
of the world. As a result the planning problem managed {\em in situ}
has traditionally remained fairly detached from low-level
control. Most adaptations at the lower-level reactive layers in
contrast are managed by specialized components (for example
\texttt{LAAS architecture} \cite{alami:1998p820,Ingrand07} and
\texttt{CLARATy} \cite{Nesnas:2003do}) that rely on different
representations for modeling local control behavior or worse do not
have any explicit formal agent behavior model. The consequent
different techniques for specifying each layer in the architecture
results in duplication of effort and a diffusion of knowledge leading
to significant design and integration issues \cite{DS1report}.
\texttt{IDEA} mitigated most of these issues by tightly integrating
planning and execution in a single representational and computational
framework with \kcomment{an} unified declarative model. Our approach
with \rx builds on this design methodology albeit in a substantially
systematic manner. The \rx architecture contributes to agent
architectures over and beyond \texttt{IDEA} in the following
\kcomment{significant} ways:

@@

\item \emph{Partitioning} the global planning problem into multiple
  decision loops, called {\em reactors}. Each reactor has its own
  scope both functionally (one for example focusing on the conversion
  of high level waypoints into low-level commands) and temporally as
  each reactor declares its planning look-ahead $\pi$ and expected
  latency $\lambda$ before being able to produce \kcomment{a} plan to
  the agent depending on where it is located in a reactor dependency
  graph such as shown in Fig. \ref{fig:agent}. A reactor closer to the
  hardware in the hierarchy, is expected to deliberate less and be
  highly responsive to observations from the world. This implies lower
  values of $\pi$ and $\lambda$ (see Section \ref{sec:arch:trex}
  below).

@@

Systematic partitioned inference is a major contribution of
\rxe. However that is not the focus of this chapter with details
covered in \cite{py10, rajan12}. Coupled interaction between planning
and the world on the other hand, has a significant implication on how
planning can be integrated in such frameworks. In this chapter we show
how using the \eu planner can be coupled to our framework by first
linking concepts in temporal planning with the \rx framework. Note
that in the following treatise, we call the formal semantic framework
of \rx as the 'agent'. Reactors constitute an entity within this agent
and are standalone blocks of inference. The scope, detail and number
of reactors are application specific and outside the scope of this
chapter.

@@

This window is used by \rx to identify when to dispatch a request to a
{\em reactor} as a new goal. This happens only if the request start
time -- represented as the interval of possible start times --
intersects this window. Requests further in the future are buffered by
the agent until this time window advances for an overlap. This
provides an elegant mechanism to request a change from the {\em
  external} state variable of a reactor while avoiding flooding the
owner reactor of this state variable.

@@

Given the above example, \rx abstracts reactor interaction by
constraining them to state variables. Each reactor is therefore
agnostic where its {\em external} state information is managed as long
as this information is available and properly maintained for managing
{\em internal} state information. This {\em internal} state in turn
may be used by other reactors. Such a formalism also constrains
reactor interaction to state information exchange which comes in two
forms as illustrated in Fig. \ref{fig:trex:flow}:

@@

\item {\em Observation on current state values}: This information
  propagates \emph{up} in the reactor dependency graph at the
  synchronization phase and occurs at the beginning of every
  tick. During this phase the agent provides updates to each reactor
  on their {\em external} state variables for this tick so they can
  compute their {\em internal} state variable values for this same
  tick. By doing so we propagate a consistent view of that state of
  the world throughout all the reactors as time
  advances. \kcomment{Observations can therefore be both sensor
    measurements as well state passed up from other reactors. The
    strict rules of timeline ownership enable a clear policy for
    conflict resolution: observations dominate expectations.}

@@

\label{sec:delib-exec-as}
\begin{figure}[!htbp]
  \centering
  \vskip-1pc
  \includegraphics[width=0.55\columnwidth]{figs/tick-cycle}
  \caption{\small \rx reactor execution cycle: {\em Deliberation} is
    interrupted by {\em synchronization} at the beginning of every
    {\em tick} allowing integration of state information.}
  \label{fig:tick-exec}
  \vskip-0.8pc
\end{figure}

@@

If they are not compatible, then {\em synchronization} identifies a
plan inconsistency. This results in the retraction of decisions made
during previous {\em deliberation} steps.  Such a relaxation can be
viewed as a backtracking allowing the reactor to identify that its
current plan has failed to execute triggering further deliberations
steps to find an alternate strategy.

Finally, when the deliberation process has identified a complete
solution for its current {\em internal} goals, a part of its plan that
applies to its {\em external} timelines is sent as a request to \rx to
handle their dispatch to corresponding reactors.  Synchronization
eventually receives {\em external } observations that confirms plan
execution, in turn recording execution progress by having the part of
the plan observed restricted to observation start times.

@@

Deliberation inside a reactor is based on \eu capabilities described
in Section \ref{sec:europa:arch}. However this deliberation comes with
some augmentation namely the reactor's deliberation latency and its
plan look-ahead both expressed in ticks and that the agent needs to
interleave deliberation with not just the synchronization but also
with deliberation of other reactors\footnote{The current
  implementation of \rx is running on a single process and it is the
  responsibility of the agent itself to emulate reactor
  multi-threading for deliberation and synchronization.}.  For this
reason while the reactor relies on the \eu solver, it slices the
execution of Algorithm \ref{alg:europa:solve} into atomic steps. This
interruption occurs around the recursive call line \ref{li:recurse}
while ensuring that the current partial plan is not inconsistant at
any single step. This is managed by allowing the call to backtrack
until a \textsf{DecisionPoInt} that is not exhausted (\ie
$decision.hasNext()$ is \texttt{true}) is found in the call stack.

A critical aspect of this deliberation step is to ensure that at the
exit of this call the $plan$ is not inconsistent. % Indeed, it is always
% possible that the next call made by the agent is for synchronization
% which could fail if the $plan$ is inconsistent before any attempt is
% made for synchronization.
If the partial plan is found to be inconsistent during a deliberation
step we either backtrack in the decision stack until a node of the
tree is found with an alternate solution or the plan is relaxed since
there is no other alternative solution. We do this by removing all
goals while keeping only recent observations.

@@

A key aspect of the \rx framework is interleaved plan and
execution. Both {\em synchronization} -- keeping track of execution --
and {\em deliberation} -- dealing with reactor planning -- of one
reactor are sharing the same {\em single} plan database which 
they modify alternatively as the \rx agent schedule their execution.

As noted above, it is synchronization which drives planning, so the
co-mingling between these two processes is critical to maintaining
state within a robot especially when it is immersed in a dynamic
environment. Further, it is important that \rx maintain
% A core aspect of this reactor is that it takes advantage of the
% specific sequencing enforced by the \rx architecture along with the
% fact that only 
one $plan$ structure shared between synchronization and planning. This
allows these two processes to not only be interleaved for agent
responsiveness, but ensures a viable mechanism to communicate.

% but also impact
% each other via plan manipulation.

As noted earlier, synchronization propagates {\em
  external} observations when a new tick occurs. Earlier, we isolated
the case when a reactor has no future goal or no plan to enforce. By
doing so we were able to develop the way we augment the \eu solver to
propagate {\em external} observations to identify {\em
  internal} state. This allowed us to focus on synchronization as a
state evaluation process that can be resolved within the \eu framework
with few extensions. Similarly we presented deliberation as an
abstraction without discussing the disruptive nature of
synchronization and how it impacts the planning process. We first
analyze the case when synchronization occurs after planning has
completed (\ie the last step of deliberation results in a plan that is
considered complete for the current look-ahead). As synchronization
starts with a plan, this deliberation will not only be a model-derived
estimation uniquely based on {\em external} observations but will also
include reactor intentions specified in the available partial plan.

@@

\begin{figure}[!b]
  \centering
  \subfloat[\small A plan produced before
  synchronization.]{\label{fig:shop:exec0}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t0}} \\
  \subfloat[\small Result of synchronization after the {\em Going}
  observation was received by the reactor with the plan showed in
    \ref{fig:shop:exec0}.]{\label{fig:shop:exec1}\includegraphics[width=.7\columnwidth]{figs/shoping_exec_t1}}
    \caption{\small The Shopping example: Tokens in {\color{red}red}
      indicate observations, tokens in {\color{blue}blue} the goal
      that this plan attempts to solve for. Arrows indicate temporal
      constraints. }
  \label{fig:shop:exec}
\end{figure}

Consider that at the next tick $\tau' = \tau+1$ the reactor managing
agent location is able to change the location state variable to
\texttt{Going}. \rx informs the reactor of this observation which is
added to the partial plan as a fact -- starting exactly at $\tau'$ and
lasting for an unknown duration which is at least one tick. As this
new observation is integrated in the plan through synchronization, the
solver can identify the similarity between this observation and the
next token in the existing plan. Instead of initiating an exhaustive
search of all possible implications, the synchronization process
starts its execution with the assumption that these new observations
are consistent with the currently maintained plan. As a consequence,
at the end of synchronization the plan depicted in Fig.
\ref{fig:shop:exec1} is likely. This is a result of propagation of
information provided by the new observation in the existing plan while
restricting the start time of \texttt{Going} and propagating temporal
constraints, making \texttt{Go} to start {\em exactly} at $\tau'$. In
doing so, the \eu solver's focus on the execution frontier ($\tau'$ in
Fig. \ref{fig:shop:exec1}) takes advantage of the existing plan to
evaluate a solution that assumes that the observation is consistent
with what was decided by the reactor.

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t1}
%   \caption{Shopping example : Result of synchronization after the {\em
%       Going} observation was received by the reactor with the plan
%     showed in Fig. \ref{fig:shop:exec0}.}
%   \label{fig:shop:exec1}
% \end{figure}

This choice is directed not only by heuristic choices made in the
solver but also enforced by the heuristic order of the decision point
resolution choices for the {\em current state flaw} shown in
Proposition \ref{prop:csf:resolve}. As noted, the first two choices
are biased towards a conservative view with respect to the existing
plan. The heuristics first attempt to extend the previous observation
for this {\em internal} timeline to avoid early commitment. If this
fails \rx attempts to start the next existing token in the plan to
advance plan execution. Both choices attempt to resolve state with the
least amount of plan perturbation by constraining further the start
and end time of existing tokens generated by previous deliberations
steps. By doing so, in a nominal situation, synchronization remains
limited to restrict time points in the plan and propagates their
impact. Most of the computational effort of creating new tokens in the
plan and scheduling them onto timelines are managed during
deliberation steps. Consequently, most of the time synchronization is
limited to very few nodes in the \eu search space often requiring no
backtracking. Fig. \ref{fig:shop:exec} shows how the existing plan can
support the synchronization process. The observation \texttt{Going}
occurring at $\tau'$ is fully compatible with the token already present
in our plan. By updating the plan and propagating equality constraints,
the resolution of the {\em current state flaw} for the {\em Agent}
timeline becomes obvious as a solution, as the token \texttt{Go} from
the plan presents itself.

@@

\begin{figure}[!b]
  \centering
  \subfloat[Conflicting Observation]{\label{fig:shop:relax1}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_relax-1}}\\
  \subfloat[Relaxed Partial Plan]{\label{fig:shop:relax2}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_relax-2}}
  \caption{\small Illustration of a conflict during synchronization
    and the resulting relaxed plan for recovery.}
\end{figure}

>>>>

A prime motivation behind the \rx architecture was to design a
controller which could bring automated planning closer to low-level
control of the vehicle while maintaining its reactivity. Traditionally
planning has been deemed computationally expensive with planner
performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for. In such a situation, the agent may thrash
\footnote{\kcomment{In such an event as the planner works towards goal
    satisfaction, the initial conditions leading to achieve that goal
    are no longer valid. The planner then tries to achieve a different
    goal which too has to be discarded similarly. And so on.}}  if the
internal state of the plan gets out of sync with the actual state of
the world.

\kcomment{A important consequence of this has been that} the planning
problem managed {\em in situ} has traditionally remained fairly
detached from low-level control. Most adaptations at the lower-level
reactive layers in contrast are managed by specialized components (for
example \texttt{LAAS architecture} \cite{alami:1998p820,Ingrand07} and
\texttt{CLARATy} \cite{Nesnas:2003do}) that rely on different
representations for modeling local control behavior or worse do not
have any explicit formal agent behavior model. The consequent
different techniques for specifying each layer in the architecture
results in duplication of effort and a diffusion of knowledge leading
to significant design and integration issues \cite{DS1report}.
\texttt{IDEA} mitigated most of these issues by tightly integrating
planning and execution in a single representational and computational
framework with \kcomment{an} unified declarative model. Our approach
with \rx builds on this design methodology albeit in a substantially
systematic manner.

The \rx architecture contributes to agent architectures over and
beyond \texttt{IDEA} in the following \kcomment{significant} ways:

@@

\item \emph{Partitioning} the global planning problem into multiple
  decision loops, called {\em reactors}. Each reactor has its own
  scope both functionally (one for example focusing on the conversion
  of high level waypoints into low-level commands) and temporally as
  each reactor declares its planning look-ahead ($\pi$) and expected
  latency ($\lambda$) before being able to produce \kcomment{a} plan
  to the agent depending on where it is located in a reactor
  dependency graph such as shown in Fig. \ref{fig:agent}. A reactor
  closer to the hardware in the hierarchy, is expected to deliberate
  less and be highly responsive to observations from the world. This
  implies lower values of $\pi$ and $\lambda$ (see Section
  \ref{sec:arch:trex} below). \kcomment{In the current design, $\pi$
    and $\lambda$ are application dependent and fixed at design time.}

@@

Systematic partitioned inference is a major contribution of
\rxe. However that is not the focus of this chapter; details are
covered in \cite{py10, rajan12}. Coupled interaction between planning
and the world on the other hand, has a substantial impact on how
planning can be integrated in such frameworks. In this chapter we show
how using the \eu planner can be coupled to the \rx framework by first
linking concepts in temporal planning with the framework. Note that in
the following treatise, we call the formal semantic framework of \rx
as the 'agent'. Reactors constitute an entity within this agent and
are standalone blocks of inference. The scope, detail and number of
reactors are application specific and outside the scope of this
chapter.

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[scale=0.35]{figs/token-disptch.pdf}
  \caption{\small \kcomment{Dispatching a token occurs only when the request
    start time overlaps a window. \texttt{Goal$_1$} therefore gets
    dispatched from \texttt{reactor$_1$} to \texttt{reactor$_2$} but
    not \texttt{Goal$_2$} to avoid early commitment.}}
  \label{fig:reactor-lookahead}
\end{figure}

This window is used by \rx to identify when to dispatch a request to a
{\em reactor} as a new goal. This happens only if the request start
time -- represented as the interval of possible start times --
intersects this window. Requests further in the future are buffered by
the agent until this time window advances for an overlap. This
provides an elegant mechanism to request a change from the {\em
  external} state variable of a reactor while avoiding flooding the
owner reactor of this state variable and avoiding early commitment.
\kcomment{Fig. \ref{fig:reactor-lookahead} illustrates an example
  between two reactors where one token is dispatched when overlapping
  the dispatch window while another is not.}

@@

Given the above example, \rx abstracts reactor interaction by
constraining them to state variables. Each reactor is therefore
agnostic where its {\em external} state information is managed as long
as this information is available and properly maintained for managing
{\em internal} state information. % This {\em internal} state in turn
% may be used by other reactors.
Such a formalism also constrains reactor interaction to state
information exchange which comes in two forms as illustrated in
Fig. \ref{fig:trex:flow}:

@@

\item {\em Observation on current state values}: This information
  propagates \emph{up} in the reactor dependency graph at the
  synchronization phase and occurs at the beginning of every
  tick. During this phase the agent provides updates to each reactor
  on their {\em external} state variables for this tick so they can
  compute their {\em internal} state variable values for this same
  tick. By doing so we propagate a consistent view of that state of
  the world throughout all the reactors as time
  advances. \kcomment{Observations can therefore be both sensor
    measurements as well as state information, passed up from other
    reactors. The strict rules of timeline ownership enable a clear
    policy for conflict resolution: observations dominate
    expectations.}

@@

\label{sec:delib-exec-as}
\begin{figure}[!htbp]
  \centering
  \vskip-1pc
  \subfloat[\small \kcomment{A view of synchronization and deliberation within a
  tick cycle.}]{\label{fig:sync-cycle}\includegraphics[width=0.35\columnwidth]{figs/sync-tick-cycle}} 
  \qquad
  \subfloat[\small A \rx reactor's execution cycle: {\em Deliberation} is
    interrupted by {\em synchronization} at the beginning of every
    {\em tick} allowing integration of state information.]{\label{fig:tick-exec}\includegraphics[width=0.45\columnwidth]{figs/tick-cycle}}
  \caption{\small \kcomment{Detailed and abstracted views of
      synchronization and deliberation within one tick cycle.}}
  \label{fig:sync-plan-cycle}
\end{figure}

@@

If they are not compatible, then {\em synchronization} identifies a
plan inconsistency. This results in the retraction of decisions made
during previous {\em deliberation} steps.  Such a relaxation can be
viewed as a backtrack, allowing the reactor to identify that its
current plan has failed to execute triggering further deliberation
steps to find an alternate strategy.

Finally, when the deliberation process has identified a complete
solution for its current goals, a part of its plan that applies to its
{\em external} timelines is sent as a request to \rx to handle their
dispatch to corresponding reactors.  Synchronization eventually
receives {\em external } observations that confirms plan execution, in
turn recording execution progress by having the part of the plan
observed restricted to observation start times.

@@

Deliberation inside a reactor is based on \eu capabilities described
in Section \ref{sec:europa:arch}. However this deliberation comes with
some augmentation, namely the reactor's deliberation latency
\kcomment{($\lambda$)} and its planning look-ahead \kcomment{($\pi$)}
both expressed in ticks. \kcomment{In addition,} the agent needs to
interleave deliberation with not just synchronization but also with
the deliberation of other reactors\footnote{The current implementation
  of \rx is running on a single process and it is the responsibility
  of the agent itself to emulate reactor multi-threading for
  deliberation and synchronization.}.  For this reason while the
reactor relies on the \eu solver, it slices the execution of Algorithm
\ref{alg:europa:solve} into atomic steps. This interruption occurs
around the recursive call line \ref{li:recurse} while ensuring that
the current partial plan is not inconsistant at any single step. This
is managed by allowing the call to backtrack until a
\textsf{DecisionPoInt} that is not exhausted (\ie $decision.hasNext()$
is \texttt{true} \kcomment{and non empty}) is found in the call
stack\footnote{\kcomment{The call stack refers to the sequence of
    recursive function calls.}}.

A critical aspect of this deliberation step is to ensure that at the
exit of this call the $plan$ is not inconsistent. % Indeed, it is always
% possible that the next call made by the agent is for synchronization
% which could fail if the $plan$ is inconsistent before any attempt is
% made for synchronization.
If the partial plan is found to be inconsistent during a deliberation
step we either backtrack in the decision stack until a node of the
\kcomment{search} tree is found with an alternate solution or the plan
is relaxed since there is no other alternative solution. We do this by
removing all goals while keeping only recent observations.

@@

A key aspect of the \rx framework is interleaved planning and
execution. Both {\em synchronization} -- keeping track of execution --
and {\em deliberation} -- dealing with reactor planning -- of one
reactor \kcomment{share} the same {\em single} plan database which
they modify alternatively as the \rx agent schedules their execution.

As \kcomment{shown in Section \ref{sec:arch:synch}}, it is
synchronization which drives planning; so the co-mingling between
these two processes is critical to maintaining state within a robot
especially when it is immersed in a dynamic environment. Further, it
is important that \rx maintain one $plan$ structure shared between
synchronization and \kcomment{deliberation}. This allows these two
processes to not only be interleaved for agent responsiveness, but
ensures a viable mechanism to communicate.

As \kcomment{also} noted earlier, synchronization propagates {\em
  external} observations when a new tick occurs. Earlier, we isolated
the case when a reactor has no future goal or no plan to enforce. By
doing so we were able to develop the way we augment the \eu solver to
propagate {\em external} observations to identify {\em internal}
state. This allowed us to focus on synchronization as a state
evaluation process that can be resolved within the \eu framework with
few extensions. Similarly we presented deliberation as an abstraction
without discussing the disruptive nature of synchronization and how it
impacts the planning process. \kcomment{That discussion occurs here in
  this section.}

We first analyze the case when synchronization occurs after planning
has completed (\ie the last step of deliberation results in a plan
that is considered complete for the current look-ahead). As
synchronization starts with a plan, this deliberation will not only be
a model-derived estimation uniquely based on {\em external}
observations but will also include reactor intentions specified in the
available partial plan.

@@

\begin{figure}[!b]
  \centering
  \subfloat[\small A plan produced before
  synchronization.]{\label{fig:shop:exec0}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t0}} \\
  \subfloat[\small Result of synchronization after the {\em Going}
  observation was received by the reactor with the plan showed in
    \ref{fig:shop:exec0}.]{\label{fig:shop:exec1}\includegraphics[width=.7\columnwidth]{figs/shoping_exec_t1}}
    \caption{\small The Shopping example: Tokens in {\color{red}red}
      indicate observations, tokens in {\color{blue}blue} the goal
      that this plan attempts to solve for \kcomment{and tokens in
        {\color{grey}grey} the result of deliberation}. Arrows
      indicate temporal  constraints \kcomment{with $==$ indicating 'equality' and $\geq$
        indicating 'greater than equal to' in timepoints}.}
  \label{fig:shop:exec}
\end{figure}

Consider that at the next tick $\tau' = \tau+1$ the reactor managing
agent location is able to change the location state variable to
\texttt{Going}. \rx informs the reactor of this observation which is
added to the partial plan as a fact -- starting exactly at $\tau'$ and
lasting for an unknown duration which is at least one tick. As this
new observation is integrated in the plan through synchronization, the
solver can identify the similarity between this observation and the
next token in the existing plan. Instead of initiating an exhaustive
search of all possible implications, the synchronization process
starts its execution with the assumption that these new observations
are consistent with the currently maintained plan. As a consequence,
at the end of synchronization the plan depicted in Fig.
\ref{fig:shop:exec1} is likely. This is a result of propagation of
information provided by the new observation in the existing plan while
restricting the start time of \texttt{Going} and propagating temporal
constraints, making \texttt{Go} to start {\em exactly} at $\tau'$. In
doing so, the \eu solver's focus on the execution frontier ($\tau'$ in
Fig. \ref{fig:shop:exec1}) takes advantage of the existing plan to
evaluate a solution that assumes that the observation is consistent
with what was decided by the reactor. \kcomment{In the event of
  inconsistency, the (plan) expectations do not match the reality;
  then partial plan failure within the reactor is initiated.} This is
directed not only by heuristic choices made in the solver but also
enforced by the heuristic order of the decision point resolution
choices for the {\em current state flaw} \kcomment{as} shown in
Proposition \ref{prop:csf:resolve}. As noted, the first two choices
are biased towards a conservative view with respect to the existing
plan.

\kcomment{\subsubsection{Dealing with partial plan failures}}
\label{sec:arch:partialfailures}

The \kcomment{solver's} heuristics first attempt to extend the
previous observation for this {\em internal} timeline to avoid early
commitment. If this fails \rx attempts to start the next token in the
plan to advance plan execution. Both choices attempt to resolve state
with the least amount of plan perturbation by constraining further the
start and end time of existing tokens generated by previous
deliberations steps. By doing so, in a nominal situation,
synchronization remains limited to restricting time points in the plan
and propagates their impact. Most of the computational effort of
creating new tokens in the plan and scheduling them onto timelines are
managed during deliberation steps. Consequently, most of the time
synchronization is limited to very few nodes in the \eu search space
often requiring no backtracking. Fig. \ref{fig:shop:exec} shows how
the existing plan can support the synchronization process. The
observation \texttt{Going} occurring at $\tau'$ is fully compatible
with the token already present in our plan. By updating the plan and
propagating equality constraints, the resolution of the {\em current
  state flaw} for the {\em Agent} timeline becomes obvious as a
solution, as the token \texttt{Go} from the plan presents itself.

@@

\begin{figure}[!b]
  \centering
  \subfloat[\small Conflicting Observation]{\label{fig:shop:relax1}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_relax-1}}\\
  \subfloat[\small Relaxed Partial Plan]{\label{fig:shop:relax2}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_relax-2}}
  \caption{\small Illustration of a conflict during synchronization
    and the resulting relaxed plan for recovery.}
\end{figure}
